\LaTeX\ Author Guidelines for ICCV Proceedings

### 2021-03-11 chapters/1_intro.tex
Small changes intro

        \end{tabular}
    \end{subtable} 
    \caption{Clustering algorithms included in the proposed \algname{} framework, given a linkage criterion, a type of graph (signed or unsigned) and the optional use of cannot-link constraints. New constrained hierarchical clustering algorithms (HCC) are highlighted in yellow. Algorithms typeset in bold-font define an ultrametric on the graph (Eq.~\ref{eq:UM_def}). Algorithms included in the green box, are weight-shift invariant (Prop.~\ref{prop:weight_shift_invariant}). 
    Given a graph $\mathcal{G}(V,E)$, we denote as $E_{ij}=(S_i \times S_{j}) \cap E$ the set of edges connecting two clusters $S_i \subseteq V$, $S_j \subseteq V$. } 
    \label{tab:linkage-criteria}
\end{table*}

@@

In this paper, we propose a simple theoretical framework that generalizes over agglomerative algorithms for signed graphs by linking them to hierarchical clustering (HC) on positive-weighted graphs \cite{lance1967general}. This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints} (see Fig.~\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}a}, \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}b}, and Table~\ref{tab:linkage-criteria}). 
We then formally prove that some of the combinations correspond to existing clustering algorithms, and introduce new algorithms for combinations which have not been explored before. By analyzing their theoretical properties, we also show which one of them define an ultrametric on the graph.

>>>>

        \end{tabular}
    \end{subtable} 
    \caption{Clustering algorithms included in the proposed \algname{} framework, given a linkage criterion, a type of graph (signed or unsigned) and the optional use of cannot-link constraints. New constrained hierarchical clustering algorithms (HCC) proposed in this paper are highlighted in yellow. Algorithms typeset in bold-font define an ultrametric on the graph (Eq.~\ref{eq:UM_def}). Algorithms included in the green box, are weight-shift invariant (Prop.~\ref{prop:weight_shift_invariant}). 
    Given a signed graph $\mathcal{G}(V,E, w_e)$, we denote as $E_{ij}=(S_i \times S_{j}) \cap E$ the set of edges connecting two clusters $S_i \subseteq V$, $S_j \subseteq V$. } 
    \label{tab:linkage-criteria}
\end{table*}

@@

Our first main contribution is a simple theoretical framework that generalizes over agglomerative algorithms for signed graphs by linking them to hierarchical clustering (HC) on positive-weighted graphs \cite{lance1967general}. This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints} (see Fig.~\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}a}, \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}b}, and Table~\ref{tab:linkage-criteria}). 
We then formally prove that some of the combinations correspond to existing clustering algorithms, and introduce new algorithms for combinations which have not been explored before. By analyzing their theoretical properties, we also show which one of them define an ultrametric on the graph.

### 2021-03-11 chapters/3_algorithm.tex
Small changes intro

Finally, in \emph{Phase~3}, the algorithm keeps merging all clusters until only a single one is left and then returns the hierarchical tree $T^*$ representing the full sequence of merging steps.
The algorithm was implemented using a standard HC implementation with computational complexity $\mathcal{O}(N^2 \log N)$ (see Appendix \ref{sec:detailed_impl} for more details).

>>>>

Finally, in \emph{Phase~3}, the algorithm keeps merging all clusters until only a single one is left and then returns the hierarchical tree $T^*$ representing the full sequence of merging steps.
The algorithm was implemented using a standard HC implementation with computational complexity $\mathcal{O}(N^2 \log N)$ (see extended details in Appendix \ref{sec:detailed_impl}).

### 2021-03-11 chapters/5_experiments_intro.tex
Small changes intro

\textbf{Grid-graphs from CNN predictions} -- We also evaluate the clustering methods on the task of neuron segmentation in EM image volumes using training data from the CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge}.
We train a 3D U-Net \cite{ronneberger2015u,cciccek20163d} using the same architecture as \cite{funke2018large} and predict long-and-short range affinities 
as described in \cite{lee2017superhuman}. The predicted affinities $a_e\in[0,1]$, which represent how likely it is for a pair of pixels to belong to the same neuron segment, are then mapped to signed edge weights $w_e=a_e-0.5$, resulting in a 3D grid-graph having a node for each pixel/voxel of the  image\footnote{To map affinities to signed weights, we also tested the \emph{logarithmic mapping} proposed in \cite{finkel2008enforcing,andres2012globally}, but it performed worse in our experiments.}. 
% \TODO{long-range 10\%} 
% Adding long-range connections to the graph is generally helpful, but when many of them carry repulsive weights. Long-range connections are more noisy. 10\% represents a good compromise.
We divided the three CREMI training samples, consisting of $\sim$196 million voxels each, into five sub-blocks for a total of 15 clustering problems (named \emph{CREMI-gridGraph} in Table~\ref{tab:datasets_and_energies}). See Appendix \ref{sec:cremi_details} for extended details about training, data augmentation, and how we remove tiny clusters after running \algname{} on the \emph{CREMI-gridGraph} clustering problems.

@@

\textbf{GASP on synthetic SSBM graphs}  -- 
% can be connected to any  that, depending on the edge-probability parameter $p$, are also \emph{dense}. 
\algname{} algorithms using cannotLinkConstraints are not expected to perform well on these graphs, because of the type of employed flip noise, so we focus our comparison only on the GAEC, HC-Avg and MWS algorithms (using Sum, Average, and AbsMax linkage methods, respectively).
Empirically, we observe that GAEC is the agglomerative algorithm performing best on SSBM graphs, almost as good as the spectral method SPONGE$_{sym}$ (see Fig.~\ref{fig:SSBM_scores}). Given the simple properties of SSBM graphs, we will now give a specific explanation of these empirical results. 
In SSBM graphs, the number of edges $E_{ij}\equiv(S_i\times S_j)\cap E$ connecting two clusters $S_i,S_j$ is  proportional to the product $|S_i|\cdot|S_j|$ of cluster sizes. 
With Sum or Avg linkage methods, due to the law of large numbers, the flipping noise is ``averaged out'' as soon as the set $E_{ij}$ becomes larger and clusters grow in size.
On the other hand, when clusters are small, it is more likely that several of the edges in $E_{ij}$ are flipped and the algorithm makes a mistake by merging two clusters belonging to different ground truth communities. From this observation, it follows that the \emph{flooding strategy} of the sum-linkage algorithm GAEC is a very good strategy on these types of graphs, because clusters are immediately grown in size (see dendrograms in Fig.~\ref{fig:dendrograms}). Average linkage method HC-Avg instead performs much worse on these graphs because it grows small equally-sized clusters and makes several wrong merge-decisions at the beginning. 
% This observation also explains the empirical results of \cite{chehreghani2020hierarchical}, which involved graph instances with very similar structure to the ones considered here. 
Lastly, the MWS algorithm is not expected to perform well on these graphs because of the high sensitivity of the AbsMax linkage to flipping noise. In Propositions \ref{prop:MWS_SSBM_1} and \ref{prop:MWS_SSBM_2} (see Appendix), we prove that on SSBM graphs the merging steps of the MWS algorithm are given by a sequence of ``coin flip'' decisions with a probability proportional to the noise parameter $\eta$, independently on the cluster sizes.

@@

\begin{figure}[t]
\begin{subfigure}[t]{0.23\textwidth}
\centering
\includegraphics[width=\textwidth,trim=0.34in 0.34in 0.34in 0.34in,clip]{./figs/SSBM_scores/summary_SSBM_experiments_k20.pdf}
\caption{$k=20$, $p=0.1$}
\end{subfigure}\hfill
\begin{subfigure}[t]{0.23\textwidth}
\centering
\includegraphics[width=\textwidth,trim=0.34in 0.34in 0.34in 0.34in,clip]{./figs/SSBM_scores/summary_SSBM_experiments_k50.pdf}
\caption{$k=50$, $p=0.2$}
\end{subfigure}
        \caption{
ARAND errors (median values over 20 experiments, lower is better) on synthetic graphs generated with SSBM, with $N=10000$ nodes, edges added with probability $p$, and $k$ ground truth communities of random size. 
% The spectral clustering methods, SPONGE and SPONGE$_sym$, were given the true number of clusters as input. 
% Solid lines represent median values over \TODO{30} experiments. Values between the 25th and the 75th percentile are shown in shaded areas.
% We report median, 25th, and the 75th percentile values over \TODO{30} experiments.
%         Scores on SSBM graphs
% \algname{} sensitivity to noise: \emph{Average} linkage proved to be the most robust. Performances are given by Rand-Score (higher is better) depending on the amount of noise added to the CNN predictions.  The two sets of experiments using under- and over-clustering noise are summarized in the plots at the top and at the bottom, respectively (see Appendix \ref{sec:appendix_noise_gen} for more details). For each experiment, some of the long-range CNN predictions were randomly selected with probability $p_{\mathrm{long}}$ and added as long-range edges to the pixel grid-graph. Experiments are performed on a crop of CREMI training sample B.
        } \label{fig:SSBM_scores}
\end{figure}

>>>>

\textbf{Grid-graphs from CNN predictions} -- We also evaluate the clustering methods on the task of neuron segmentation in EM image volumes using training data from the CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge}.
We train a 3D U-Net \cite{ronneberger2015u,cciccek20163d} using the same architecture as \cite{funke2018large} and predict long-and-short range affinities 
as described in \cite{lee2017superhuman}. The predicted affinities $a_e\in[0,1]$, which represent how likely it is for a pair of pixels to belong to the same neuron segment, are then mapped to signed edge weights $w_e=a_e-0.5$, resulting in a 3D grid-graph having a node for each pixel/voxel of the  image\footnote{To map affinities to signed weights, we also tested the \emph{logarithmic mapping} proposed in \cite{finkel2008enforcing,andres2012globally}, but it performed worse in our experiments.}. 
% \TODO{long-range 10\%} 
% Adding long-range connections to the graph is generally helpful, but when many of them carry repulsive weights. Long-range connections are more noisy. 10\% represents a good compromise.
We divided the three CREMI training samples, consisting of $\sim$196 million voxels each, into five sub-blocks for a total of 15 clustering problems (named \emph{CREMI-gridGraph} in Table~\ref{tab:datasets_and_energies}). See Appendix \ref{sec:cremi_details} for extended details about training, data augmentation, and how we remove tiny clusters left after running \algname{} on the \emph{CREMI-gridGraph} clustering problems.

@@

\textbf{GASP on synthetic SSBM graphs}  -- 
% can be connected to any  that, depending on the edge-probability parameter $p$, are also \emph{dense}. 
\algname{} algorithms using cannotLinkConstraints are not expected to perform well on these graphs, because of the type of employed flip noise, so we focus our comparison only on the GAEC, HC-Avg and MWS algorithms (using Sum, Average, and AbsMax linkage methods, respectively).
Empirically, we observe that GAEC is the agglomerative algorithm performing best on SSBM graphs, almost as good as the spectral method SPONGE$_{sym}$ (see Fig.~\ref{fig:SSBM_scores}). Given the simple properties of SSBM graphs, we will now give a specific explanation of these empirical results. 
In SSBM graphs, the number of edges $E_{ij}\equiv(S_i\times S_j)\cap E$ connecting two clusters $S_i,S_j$ is  proportional to the product $|S_i|\cdot|S_j|$ of cluster sizes. 
With Sum or Avg linkage methods, due to the law of large numbers, the flipping noise is ``averaged out'' as soon as the set $E_{ij}$ becomes larger and clusters grow in size.
On the other hand, when clusters are small, it is more likely that several of the edges in $E_{ij}$ are flipped and the algorithm makes a mistake by merging two clusters belonging to different ground truth communities. From this observation, it follows that the \emph{flooding strategy} of the sum-linkage algorithm GAEC is a very good strategy on these types of graphs, because clusters are immediately grown in size (see dendrograms in Fig.~\ref{fig:dendrograms}). Average linkage method HC-Avg instead performs much worse on these graphs because it grows small equally-sized clusters and makes several wrong merge-decisions at the beginning. 
% This observation also explains the empirical results of \cite{chehreghani2020hierarchical}, which involved graph instances with very similar structure to the ones considered here. 
Lastly, the MWS algorithm is not expected to perform well on these graphs because of the high sensitivity of the AbsMax linkage to flipping noise. In Propositions \ref{prop:MWS_SSBM_1} and \ref{prop:MWS_SSBM_2} (see \TODO{Appendix}), we prove that on SSBM graphs the merging steps of the MWS algorithm are given by a sequence of ``coin flip'' decisions with a probability proportional to the noise parameter $\eta$, independently on the cluster sizes.

@@

\begin{figure}[t]
\begin{subfigure}[t]{0.23\textwidth}
\centering
\includegraphics[width=\textwidth,trim=0.34in 0.34in 0.34in 0.34in,clip]{./figs/SSBM_scores/summary_SSBM_experiments_k20.pdf}
\caption{$k=20$, $p=0.1$}
\end{subfigure}\hfill
\begin{subfigure}[t]{0.23\textwidth}
\centering
\includegraphics[width=\textwidth,trim=0.34in 0.34in 0.34in 0.34in,clip]{./figs/SSBM_scores/summary_SSBM_experiments_k50.pdf}
\caption{$k=50$, $p=0.2$}
\end{subfigure}
        \caption{
ARAND errors (median values over 20 experiments, lower is better) on synthetic graphs generated with SSBM. We consider $k$ ground truth communities of random size. Graphs have $N=10000$ nodes and edges are randomly added with probability $p$. 
% The spectral clustering methods, SPONGE and SPONGE$_sym$, were given the true number of clusters as input. 
% Solid lines represent median values over \TODO{30} experiments. Values between the 25th and the 75th percentile are shown in shaded areas.
% We report median, 25th, and the 75th percentile values over \TODO{30} experiments.
%         Scores on SSBM graphs
% \algname{} sensitivity to noise: \emph{Average} linkage proved to be the most robust. Performances are given by Rand-Score (higher is better) depending on the amount of noise added to the CNN predictions.  The two sets of experiments using under- and over-clustering noise are summarized in the plots at the top and at the bottom, respectively (see Appendix \ref{sec:appendix_noise_gen} for more details). For each experiment, some of the long-range CNN predictions were randomly selected with probability $p_{\mathrm{long}}$ and added as long-range edges to the pixel grid-graph. Experiments are performed on a crop of CREMI training sample B.
        } \label{fig:SSBM_scores}
\end{figure}
